Random Forests

### 2020-07-02 pkg/partykit/inst/ULGcourse-2020/slides_forest.Rnw
further revisions on section 'implementations'
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/partykit@3032 255f4249-2263-4417-b1ea-8498779e27a7

Former-commit-id: 40e22e04e03b698bfab52584bd8165bbb1641efc

{\bf randomForest:}
\begin{itemize}
  \item R package for classic random forests.
  \item Based on implementations of CART.
\end{itemize}

@@

@@

{\bf ranger}:
\begin{itemize}
\item RANdom  forest  GEneRator.
\item R package providing a faster implementation of classic random forests.
\end{itemize}

<<call_ranger, eval=FALSE, echo=TRUE>>=
rf <- ranger(log(wage) ~ education + experience + age + ethnicity + gender + union,
             data = CPS1985)
@

@@

{\bf partykit:}
\begin{itemize}
  \item R package offering a toolkit for unbiased recursive partitioning. 
  \item Provides the forest-building function \fct{cforest}, based on conditional inference trees.
\end{itemize}

<<call_cforest, eval = FALSE>>=
cf <- cforest(log(wage) ~ education + experience + age + ethnicity + gender + union,
              data = CPS1985)
@

\only<1>{
Optional forest-specific control arguments:
\begin{itemize}
\item \code{ytrafo}: transformation function applied to the response,
\item \code{ntree}: nr. of trees, 
\item \code{mtry}: nr. of randomly sampled split variable candidates, 
\item \code{perturb}: type and size of subsetting, 
\item \ldots 
\end{itemize}
\vspace{0.9cm}
}
\only<2>{
Optional tree-specific arguments handed over via \fct{ctree\_control}:
\begin{itemize}
\item \code{minsplit}: minimum nr. of observations to perform a split, 
\item \code{minbucket}: minimum nr. of observations in a node after splitting, 
\item \code{maxdepth}: maximum depth of the tree, 
\item \code{alpha}: significance level for split variable selection,
\item \ldots 
\end{itemize}
\vspace{0.9cm}
}
\end{frame}

@@

{\bf Predictions:} For a (possibly new) set of observations the method \fct{predict} can be employed to obtain the corresponding predicted values of the response variable.

For a ranger object:
<<call_predict_rf, eval=FALSE, echo=TRUE>>=
predict(rf, data = testdata)
@

For a cforest object:
<<call_predict_cf, eval=FALSE, echo=TRUE>>=
predict(cf, newdata = testdata)
@

@@

\textbf{Further R packages:}
%
\begin{itemize}
  \item grf (generalized random forests),
  \item disttree (distributional forests, based on partykit),
  \item \ldots
\end{itemize}

>>>>

{\bf randomForest:}
\begin{itemize}
  \item R package for classic random forests.
  \item Based on implementations of CART.
  \item First implementation of random forests in R.
\end{itemize}

@@

{\bf ranger}:
\begin{itemize}
\item RANdom  forest  GEneRator.
\item R package providing a fast implementation of classic random forests.
\end{itemize}

{\bf partykit:}
\begin{itemize}
  \item R package offering a toolkit for unbiased recursive partitioning. 
  \item Provides the forest-building function \fct{cforest}, based on conditional inference trees (Ctree).
\end{itemize}

@@

{\bf ranger}:

<<call_ranger, eval=TRUE, echo=TRUE>>=
library("ranger")
rf <- ranger(log(wage) ~ education + experience + age + ethnicity + gender + union,
             data = CPS1985)
@

@@

{\bf ranger}:

<<call_ranger_predict, eval=TRUE, echo=TRUE, results=verbatim>>=
newdata <- data.frame(education = 13, experience = 17,
                      age = 36, ethnicity = "cauc",
                      region = "other", gender = "male",
                      occupation = "worker", sector = "other",
                      union = "no", married = "yes")
pred_rf <- predict(rf, data = newdata)
pred_rf$predictions     
exp(pred_rf$predictions)     
@

@@

{\bf partykit:}

<<call_cforest, eval = FALSE, echo=TRUE>>=
library("partykit")
cf <- cforest(log(wage) ~ education + experience + age + ethnicity + gender + union,
              data = CPS1985)
@

\only<1>{
Optional forest-specific control arguments:
\begin{itemize}
\item \code{ytrafo}: transformation function applied to the response,
\item \code{ntree}: number of trees, 
\item \code{mtry}: number of randomly sampled split variable candidates, 
\item \code{perturb}: type and size of subsetting, 
\item \ldots 
\end{itemize}
%\vspace{0.9cm}
}
\only<2->{
Optional tree-specific arguments handed over via \fct{ctree\_control}:
\begin{itemize}
\item \code{minsplit}: minimum number of observations to perform a split, 
\item \code{minbucket}: minimum number of observations in a node after splitting, 
\item \code{maxdepth}: maximum depth of the tree, 
\item \code{alpha}: significance level for split variable selection,
\item \ldots 
\end{itemize}
%\vspace{0.9cm}
}

% \only<3>{
% <<call_cforest_control, eval = FALSE, echo=TRUE>>=
% cf <- cforest(log(wage) ~ education + experience + age + ethnicity + gender + union,
%              data = CPS1985, control = ctree_control(minsplit = 20))
% @
% }

{\bf partykit:}

<<call_cforest_predict, eval = TRUE, results=verbatim>>=
newdata <- data.frame(education = 13, experience = 17,
                      age = 36, ethnicity = "cauc",
                      region = "other", gender = "male",
                      occupation = "worker", sector = "other",
                      union = "no", married = "yes")
pred_cf <- predict(cf, newdata = newdata)
pred_cf
exp(pred_cf)
@

@@

\textbf{Further R packages:}
%
\begin{itemize}
  \item grf: generalized random forests,
  \item disttree: distributional forests, based on partykit,
  \item \ldots
\end{itemize}
